Using Probabilistic Knockoffs of Binary Variables to Control the False Discovery Rate

### 2015-07-29 masters_paper/presentation.tex
Getting to mu conditionals

\begin{frame}{Random Binary Knockoffs}
    \begin{itemize}
        \item A useful 
    \end{itemize}
\end{frame}

>>>>

\begin{frame}{Random Binary Notation}
    \begin{itemize}
        \item Binary data is common in data analysis and a much more manageable family of distributions.
        \item We can think of observations in $X$ as observations of random binary vector $\mathbf x\in\{0,1\}^p$.
        \item The full family for $\mathbf x$ is multinomial on $2^p$ outcomes.
        \item Still useful to consider first two moments: 
            \[ \E(\mathbf x) = \mathbf{m} \in [0,1]^p \quad \& \quad \E(\mathbf{x}\mathbf{x}^T) = M \in [0,1]^{p\times p} \]
        \item For arbitrary $M$ to correspond to a random binary vector, must be case that $ M-\mathbf{m}\mathbf{m}^T = \Sigma \succeq0$
            \[\max\{0,m_i+m_j -1\} \leq M_{ij} \leq \min\{m_i,m_j\} \]

    \end{itemize}
\end{frame}

\begin{frame}{Random Binary Knockoffs}
    \begin{itemize}
        \item Integer programing is np-hard, making finding finding $\tilde X\in\{0,1\}^{n\times p}$ to fit correlations exactly difficult. 
        \item Instead, introduce a relaxed problem where $\tilde X\st X$ is drawn randomly such that, where $\Sigma=\cov(\mathbf x)$
            \[ \cov(\mathbf{\tilde x}, \mathbf x) = \Sigma - \diag{\mathbf s} \quad \& \quad \cov(\mathbf{\tilde x}) = \Sigma \]
        \item Almost same correlation condition as before, just only holds in expectation.
        \item Switch from Gramian matrix to correlation matrix makes moment condition less likely to be violated. 
    \end{itemize}
\end{frame}

\begin{frame}{Quadratic Programing}
    \begin{itemize} 
        \item Simplest approach to Random Binary Knockoffs is to draw the entries of $\tilde X$ independently based on $P\in[0,1]^{n\times p}$.
        \item The best possible $P$ for the task would satisfy
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|X^TP-(M-\diag{s})\|_{fro}^2 + \sum_{i\neq j}(P_i^T P_j - M_{ij})^2 $\\
                    subject to   & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}
        \item Can be formulated as a quadratic program with slack variables
            \begin{center}
                \begin{tabular}{r l}
                    minimize     & $\|W\|_{fro}^2 + \|V\|_{fro}^2 $ \\
                    subject to   & $ -W \leq X^TP-(M-\diag{s})\leq W $ \\
                                 & $ -V_{ij} \leq P_i^T P_j - M_{ij} \leq V_{ij} \quad \forall i\neq j$ \\
                                 & $ \mathbf 1^T P = \mathbf m $ \\
                                 & $0 \leq P \leq 1$
                \end{tabular} 
            \end{center}
        \item Huge optimization problem, likely computationally impractical.

    \end{itemize}
\end{frame}
